Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex
more edits

\subsection{Personal Electronic Sensors}
There has been a surge in popularity of personal electronic sensors as
part of the ``quantified-self'' movement to measure and improve one's health.
Wireless sensors such as the Fit-bit and Nike FuelBand and small and discreet,
yet provide the wearer with a wealth of information about their own activity level.
In particular, wearers have a desire to improve their health and fitness, based on
the feedback they receive from their device.

The measurements from such devices are of particular interest because of the
frequency and granularity of measurement that they perform - showing minute-by-minute updates
throughout the day, with no clinical involvement.

@@

>>>>

\subsection{Automatic activity sensing and digital well-being}
The recent proliferation in personal wearable activity sensors and
network and storage- enabled digital health measurement devices has
been driven by both the falling costs of embeddable electronics, and
the demand for self-measurement from the ``quantified-self''\cite{}
movement.  Wireless sensors such as the Fit-bit\cite{} and Nike
FuelBand\cite{} and small, discreet, and low-cost, providing the
wearer with high-resolution temporal data about their activity levels,
with little or no effort.

@@

\section{Storing activity diaries}

\section{Representing activity diaries}

\section{Privacy Controls}

\section{Conclusion}

\section{Biographies}
